Methods for Large Scale Learning to Rank

### 2014-04-24 report/Chapters/LTRMethods.tex
fenchelrank geupdate

Let $D(w) = -G(w)$, then the objective function stated in \ref{eq:pairwise_l1_loss} can be rewritten as shown in Equation \ref{eq:fenchel_dual}.
\begin{equation}
\max_w D(w) = \max_w I_{||w||_{1} \le 1}(w) - \frac{r^2}{p} \sum\limits_{i=1}^{p}\max(0,\frac{1}{r}-(Kw)_i)^2
\label{eq:fenchel_dual}
\end{equation}

>>>>

\noindent Let $D(w) = -G(w)$. This allows the FenchelRank objective function (Equation \ref{eq:pairwise_l1_loss}) to be rewritten using Fenchel's duality theorem (Equation \ref{eq:fenchel_duality_theorem}) to the form shown in Equation \ref{eq:fenchel_dual}.
\begin{equation}
\max_w D(w) = \max_w I_{||w||_{1} \le 1}(w) - \frac{r^2}{p} \sum\limits_{i=1}^{p}\max(0,\frac{1}{r}-(Kw)_i)^2
\label{eq:fenchel_dual}
\end{equation}
